\documentclass{article}
\renewcommand{\familydefault}{phv}

\usepackage{fancyhdr}
\usepackage[letterpaper,top=1in, bottom=1in, outer=1in, inner=1in]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage{vwcol}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{tabularx}

\pagestyle{fancyplain}

\setlength\headheight{43.28pt}
\setlength\headsep{10pt}
\setlength\parindent{0pt}
\setlength\multicolsep{0pt}

%%
%% Header 
%%
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{
  \begin{tabular}{l}
    \\
    \textcolor{Mahogany}{matt@tretin.net}\\
    \textcolor{MidnightBlue}{203.247.0623}\\
  \end{tabular}
}
\fancyhead[C]{
  \begin{tabular}{c}
    \\
    \textcolor{Black}{\textbf{{\LARGE Matt Tretin}}}\\
    \\
  \end{tabular}
}
\fancyhead[R]{
  \begin{tabular}{r}
    123 East 82$^{\mbox{nd}}$ St.\\
    Apt. 3D\\
    New York NY, 10028\\
    %% \textcolor{Black!80}{123 East $82^{\mbox{nd}}$ St.}\\
    %% \textcolor{Black!80}{Apt 3D}\\
    %% \textcolor{Black!80}{New York NY, 10028}\\
  \end{tabular}
}

\begin{document}
%%
%% Personal Statement 
%%
I'm an experienced (10+ years) engineering manager, systems
architect, technical lead and software engineer. I specialize in
greenfield development, innovation, micro-service architectures and
online video distribution systems. I believe engineering is a
discipline driven by making decisions based on data.

\textit{Seeking director and management level roles. References available upon request.}

%%
%% Patents 
%%
\vspace{10pt}\textbf{Patents}

\vspace{5pt}\begin{small}
\begin{itemize}[nosep,label=,leftmargin=*]
\item USPTO 10,440,367 - Systems and Methods for Adaptively Encoding Video Streams
\item USPTO 10,419,786 - Systems and Methods for Securely Generating Live Previews
\item USPTO 20200099974 - Systems And Methods For Generating Individualized Playlists - {\tiny PENDING}
\item USPTO 16/836,700 - Fast Video Stream Startup - {\tiny PENDING}
\end{itemize}
\end{small}

%%
%% Technologies 
%%
\vspace{10pt}\textbf{Technologies}

\vspace{5pt}\begin{multicols}{2}
  \begin{small}
    %%\begin{itemize}[nosep,label={\tiny$\rightarrow$},leftmargin=*]
    \begin{itemize}[leftmargin=*,label=]
    \item\begin{minipage}[t]{\linewidth}{\textit{Languages:} Go, Java, C, LUA, JS, Bash, Python, Lisp, OCaml}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{\textit{AWS:} EC2, Lambda, S3, Glacier, SQS, SMS, SNS, RDS, ElastiCache, VPC, CloudFront,
      Route 53, CloudWatch, CloudFormation, CloudTrail, MediaTailor, Athena, EMR, Glue, IAM, KMS, ECR, EKS, ECS}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{\textit{GCP:} Compute Engine, Cloud Storage, GKE, BigQuery, Cloud Load Balancing,
      Cloud Monitoring, Pub/Sub, IAM, Container Registry, G Suite}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{\textit{Databases:} MySQL, Postgres, MongoDB, Redis, Cassandra, Sleepycat/XmlDB, Jena}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{\textit{Queuing:} Kafka, NATS, RabbitMQ, ActiveMQ}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{\textit{Management:} Hybrik, Concourse, Vault, Zookeeper, Chronos}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{\textit{Data:} Hadoop, Spark}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{\textit{Software:} IDEA Suite, JIRA, Confluence, PivotalTracker,
      Emacs, Vim, Gnuradio, Maltego/Paterva, \LaTeX}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{\textit{GNU/Linux:} Arch, Debian, Ubuntu, LFS}\end{minipage}
    \end{itemize}
  \end{small} 
\end{multicols}

%%
%% Roles 
%%
\vspace{10pt}\textbf{Roles}

%%
%% Pluto TV
%%
\vspace{5pt}\begin{tabularx}{\textwidth}{@{}lllXr}
  Apr. 2019 - Present&\textcolor{Mahogany}{Pluto TV}&\textcolor{Black!80}{New York, NY}&&\textcolor{MidnightBlue}{Engineering Manager Video Systems}
\end{tabularx}

\vspace{3pt} I manage 3 engineering teams of 4-6 people each and report directly to the VP of Engineering. My teams are responsible for
all transcoding, video streaming, and ad insertion operations.
\begin{multicols}{2}
  \begin{small}
    \begin{itemize}[leftmargin=*,label=\tiny{$\bullet$}]
    \item\begin{minipage}[t]{\linewidth}{Design and PoC of next-generation CMAF video ingestion workflow and JIT packaging workflow.
        Designed DRM, 4K, and multi-ABR ladder solutions.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Designed and launched new way to serve VOD assets with HLS. The company sought a patent on this work.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Introduced StatsD and SignalFX to monitor all video services 24/7. Setup monitoring
        and alerting with PagerDuty.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Refactored approach to error handling and logging to uncover dozens of long existing unknown defects.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Oversee the management of over 700 EC2 instances running more than 3.5K containers.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Transitioned the entire video stack to ephemeral, immutable infrastructure with Terraform.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Introduced the concepts of service timeouts, back-offs and operational degraded state, to prevent cascade failures.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Rebuilt CI/CD workflows to enable automated deployments.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Built out all 3 teams starting with only 1 employee.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Hold regular one-on-ones with all team members, review PRs and set coding standards.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Plan road-map initiatives, sprints, and epics. Work with product leads from other teams.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Facilitate all regular agile meetings: scrum, planning, grooming, and retrospective.}\end{minipage}
    \end{itemize}
  \end{small} 
\end{multicols}

%%
%% Integral Ad Science (IAS) 
%%
\vspace{15pt}\begin{tabularx}{\textwidth}{@{}lllXr}
  Sep. 2018 - Apr. 2019&\textcolor{Mahogany}{Integral Ad Science}&\textcolor{Black!80}{New York, NY}&&
  \begin{minipage}[t]{1.9in}{\textcolor{MidnightBlue}{Team Lead \& Manager OTT Measurement}}\end{minipage}
\end{tabularx}

\vspace{3pt} I managed a team of 6 engineers reporting to a Director of Engineering. My team was responsible for designing, building, and
launching IAS's OTT ad-verification and measurement solution. 
\begin{multicols}{2}
  \begin{small}
    \begin{itemize}[leftmargin=*,label=\tiny{$\bullet$}]
    \item\begin{minipage}[t]{\linewidth}{Successfully applied agile principles to bring an out of control project on track to meet a hard customer deadline.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Worked with the data science team to create a new fraud detection algorithm appropriate for server side ad beaconing.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Was the principal architect for migrating all the teams services from on-prem infrastructure to AWS.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Hold regular 1-1s with all team members, and worked with a scrum master to facilitate all agile ritual meetings.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Worked with a product manager to plan epics and road-map initiatives according to SAFe.}\end{minipage}
    \end{itemize}
  \end{small} 
\end{multicols}

\pagebreak 
%%
%% FuboTV 
%%
\begin{tabularx}{\textwidth}{@{}lllXr}
  Oct. 2016 - Sep. 2018&\textcolor{Mahogany}{FuboTV}&\textcolor{Black!80}{New York, NY}&&\textcolor{MidnightBlue!75}{Senior Software Engineer}\\
  &&&&\textcolor{MidnightBlue}{\begin{minipage}[t]{2in}{Manager Video Quality, Switching/Signaling, Video Operations}\end{minipage}}\\
\end{tabularx}

\vspace{3pt} I managed 3 teams of 4-8 engineers each reporting directly to the CTO. My teams were responsible for 24/7 ingestion and per-chunk indexing of
over 1500 HLS video feeds, per-user playlist generation, mid-stream video switching, scheduling systems, and enforcing geofencing and blackout restrictions. 

\begin{multicols}{2}
  \begin{small}
    \begin{itemize}[leftmargin=*,label=\tiny{$\bullet$}]
    \item\begin{minipage}[t]{\linewidth}{Was principal architect and lead engineer for all video services company wide.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Implemented in-stream HLS switching, geo-fencing, and blackout restrictions.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Implemented cloud DVR system.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Implemented SCTE224/SCTE35 based signaling and switching system to integrate with 3rd party systems defining stream availability.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Implemented in-house switching data systems to define geographic and time based limitations on stream availability.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Implemented a suite of QA tools to diagnose, triage, and reproduce video stream issues.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Implemented a GoLang wrapper around core FFMpeg functions to easily use the tool as part of backend services.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Implemented system to securely generate preview streams for inclusion in ``live'' advertisements for the company.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Created 30+ hardware devices to down-link OTA (over-the-air) channels and securely back hual them to FuboTV systems for distribution.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Created load tests capable of generating about 500K concurrent users worth of load and ensured all systems could sustain it.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{I was the first video engineering hire, built out 3 teams with about 15 people underneath me.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Hold regular one-on-ones with all team members, review PRs and set coding standards.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Plan road-map initiatives, sprints, and epics. Work with product leads from other teams.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Facilitate all regular agile meetings: scrum, planning, grooming, and retrospective.}\end{minipage}
    \end{itemize}
  \end{small} 
\end{multicols}

%%
%% Perka
%%
\vspace{15pt}\begin{tabularx}{\textwidth}{@{}llXr}
  Jun. 2015 - Aug. 2016&\textcolor{Mahogany}{Perka}&&\textcolor{MidnightBlue}{Senior Software Engineer}
\end{tabularx}

\vspace{3pt} I was a senior software engineer on the backend team. I reported directly to a Team Lead \& Manager. The backend team was reponsible for all server-side components of the application. 
\begin{multicols}{2}
  \begin{small}
    \begin{itemize}[leftmargin=*,label=\tiny{$\bullet$}]
    \item\begin{minipage}[t]{\linewidth}{Re-factored and migrated all user management systems for a legacy code-base.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Re-architect all backend database communications and systems to migrate from Cassandra to Postgres.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Migrated all backend systems from a custom data abstraction layer to JPA annotations on POJOs.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Created several coding challenge questions and automated evaluation system to aid in the hiring process.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Created organizational standards around error handling to enforce a consistent view of defects.}\end{minipage}
    \end{itemize}
  \end{small} 
\end{multicols}

%%
%% ESPN
%%
\vspace{15pt}\begin{tabularx}{\textwidth}{@{}lllXr}
  September 2018 - April 2019&\textcolor{Mahogany}{ESPN}&\textcolor{Black!80}{Bristol, CT}&&\textcolor{MidnightBlue}{Associate Development Engineer}
\end{tabularx}

\vspace{3pt} I was on the Technology \& Innovation team, I reported directly to an Associate Director of Engineering. The Technology \& Innovation team was tasked with short term strategic projects,
innovation initiatives, and experimental projects to help asses the value of various kinds of new technologies. 
\begin{multicols}{2}
  \begin{small}
    \begin{itemize}[leftmargin=*,label=\tiny{$\bullet$}]
    \item\begin{minipage}[t]{\linewidth}{Implemented a tool to visualize and compare any two umpires strike zones across any to points in time. This was turned into an on-air telestration tool.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Ported ESPN's TotalQBR calculations from VB script in an Excel spreadsheet to raw VB code for use in driving on air graphics systems.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Designed a basic algorithm to create play-by-play text from baseball game play by play data.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Designed and implemented an algorithm to send notifications on AMQP queue for all program changes and commercial break start and end events.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Implemented a custom HLS video server to re-construct HLS feeds between any two points in time.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Designed and implemented a public API for users to submit play-by-play data about non-professional sports.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Implemented ESPN's twitter integration for Windows 10.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Helped perform technical due-diligence on several potential acquisitions.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Designed and implemented a PoC semantic-web database to power a next generation content management system.}\end{minipage}
    \end{itemize}
  \end{small} 
\end{multicols}

\pagebreak
%%
%% UVM
%%
\vspace{15pt}\begin{tabularx}{\textwidth}{@{}lllXr}
  Jan. 2007 - Dec. 2009&\textcolor{Mahogany}{UVM Complex Systems Center}&\textcolor{Black!80}{Burlington, VT}&&\textcolor{MidnightBlue}{Student Researcher}
\end{tabularx}

\vspace{3pt} Research in social networks, complex systems, and automated  emotional classification of online text.
We were the first team to measure the happiness of Twitter in real time. The team's work was covered in the New York Times and published as a letter to the journal Nature.
\begin{multicols}{2}
  \begin{small}
    \begin{itemize}[leftmargin=*,label=\tiny{$\bullet$}]
    \item\begin{minipage}[t]{\linewidth}{Wrote data ingest system to perform sentiment analysis of Twitter fire-hose.}\end{minipage}
    \item\begin{minipage}[t]{\linewidth}{Wrote a language classification tool to detect English and Spanish language tweets.}\end{minipage}
    \end{itemize}
  \end{small} 
\end{multicols}

%%
%% Certificates
%%
\vspace{10pt}\textbf{Cerficates}

\vspace{3pt}\begin{tabular}{lll}
  2011 & JavaSepcialists.eu & Java Specialist Master\\
  2011 & JavaSepcialists.eu & Java Concurrency Specialist
\end{tabular}

%%
%% Education
%%
\vspace{10pt}\textbf{Education:}

\vspace{3pt}\begin{tabular}{lll}
  2006 - 2010 & University of Vermont & Computer Science \& Philosophy\\
  2000 - 2004 & Weston High School &  \\
  2002 &  HCSSiM & \\
  2003 &  HCSSiM & \\ 
\end{tabular}


%% \job{Jun 2015}{Aug 2016}{Perka}{Software Engineer}{I was part of the team
%%   responsible for maintenance and design of stable, performant, mission critical
%%   backend systems. My work focused on finding a safe way to migrate all
%%   production data from a custom relational data system built on top of Cassandra
%%   to PostgreSQL.}

%% \job{Jan 2015}{March 2015}{ESPN}{Data Platforms \& Architecture - Development
%%   Engineer}{Data Platforms \& Architecture group was responsible for the design,
%%   implementation, maintenance, and ongoing operation of production APIs
%%   leveraging a diverse set technologies meant to increase the efficacy of human
%%   users (butts-in-chairs) during the lifecycle of content creation and
%%   distribution both in-house and from remote locations.}

%% \job{Oct 2010}{Jan 2015}{ESPN}{Technology Innovation Team - Associate
%%   Development Engineer}{The Innovation Group's charter was to prototype a vision
%%   of how ESPN might look 3-5 years out by pushing current technologies to their
%%   absolute limit. Consider ESPN a factory for data about sports rather than a TV
%%   network. That data comes in many forms: 24x7 live-linear streams, clips,
%%   shows, web pages, database tables, etc. The innovation team devised new ways
%%   of connecting these disparate sources of data to create compelling end-user
%%   experiences and new capabilities for in house tooling.}

%% \job{Jan 2008}{Dec 2009}{Peak Systems}{Technician}{Provided on-site
%%   troubleshooting and repair for desktop PC systems (hardware), 3rd-party
%%   software, Microsoft Products, networking, etc. for secure data entry
%%   facilities on air-gapped networks.}






%% \project{Video Ad Live Preview Service}{I was responsible for the design,
%%   implementation, and ongoing operation of a custom video server enabling the
%%   marketing department to embed live (i.e. the World Cup game going on right
%%   now) video previews as both HTML5 ad pods and a custom embeddable widget for
%%   affiliate marketing sites. This lowered our average customer acquisition cost
%%   from the many tens of dollars to less than five. These campaigns converted
%%   impressions in record numbers and were the start of the funnel for more for
%%   than half of all new customers during the 2018 World Cup.}

%% \project{Video Stream Asset Twiddler}{I was responsible for the design and
%%   initial implementation of a custom video server providing HLS and DASH streams
%%   that break in predictable ways. This enabled test automation with consistent
%%   input and output expectations across multiple disparate platforms: Web, IOS,
%%   TvOS, Roku, Android, Chromecast, and FireTV. By creating tests with the same
%%   input and expected results for each platform, differences in player
%%   implementations, behaviors, and metric reporting became clearly identifiable
%%   and therefore fixable.}

%% \project{GEFF: Go Encapsulated FFMpeg}{I responsible for the design and
%%   implementation CGo library that encapsulated many common FFMpeg workflows,
%%   including PTS, DTS continuity analysis, muxing and demuxing of various program
%%   streams, PSNR analysis, etc. This was done by using the libav C libraries
%%   directly, not by wrapping the FFMpeg CLI enabling us to build efficient HTTP
%%   based microservers to manage these workflows.}

%% \project{Video Ingest}{A 24x7x365 ingest service responsible for the storage and
%%   time-wise indexing of over 1000 video streams for live distribution (about 14
%%   seconds behind cable)}

%% \project{Video Playlist Server}{A in-house HLS service providing both live and
%%   time-shifted access to video content. This service is regularly (automated)
%%   load tested to more than 500,000 concurrent users and has seen in upwards of
%%   100,000 concurrent users in production}

%% \project{SCTE224 \& MIMS (Manual Ingest Mapping System)}{FuboTV had the first
%%   commercially available SCTE224 data system for integrating with the MCRs
%%   (master control rooms) of broadcast partners. Basically, this system allows
%%   broadcasters like Fox and NBC to define which stations (i.e. local Fox in NY
%%   is not the same channel, content, incorporation, etc. as the local Fox in
%%   Pittsburg) receive which video streams by seamlessly integrating into their
%%   current production workflows in real time. For broadcast partners that did not
%%   yet have this technology available, we created a manual system for our
%%   programming and content teams to use.}

%% \project{A New Architecture}{I was a principal architect helping to design a
%%   top-to-bottom web-stack built from well known open source solutions meant to
%%   replace an ailing custom codebase. The system we were replacing consisted of a
%%   database, web server, and an event dispatch/event handling mechanism -- all of
%%   which were custom built. The system was full of very ugly patches, leaky
%%   abstraction, and was difficult to modify. Switching to battle-tested open
%%   source solutions allowed us to eliminate 72\% of the current codebase without
%%   compromising any functionality. In addition, we decreased the number of AWS
%%   instances needed to run a complete stack by an order of magnitude. In order to
%%   migrate the data, raw data blobs from the custom database needed to be
%%   translated to a properly relational set of SQL records and tables. I was the
%%   sole engineer tasked with writing this migration utility. The biggest
%%   challenges were translating an object graph where logical equality was
%%   sufficient to object graphs where object equality was required, de-tabling
%%   almost four years of object-reference rot, and be performant enough to crunch
%%   just over 100GB of data in under twenty minutes}

%% \project{Umpire Strike Zone Visualizer}{The Innovation Group was asked to
%%   prototype a visualization tool allowing a user to compare the “average”
%%   strike-zone of any two major league umpires across an arbitrary dimension from
%%   a predefined set, i.e. the same the same player, or team, etc. The
%%   visualization showed a heat-map of an MxN grid representing a region larger
%%   than the strike zone. Cells in the grid where colored to show whether more
%%   pitches in that cell were balls or strikes, showing the derived strike zone as
%%   a gradient and the defined strike zone as a superimposed box}

%% \project{TV2016}{In order to understand how our product (a cable TV network)
%%   could be adapted to leverage at-home IP video distribution technologies, the
%%   Innovation Team was tasked with inventing the “cable box” for an IP-multicast
%%   based TV distribution network. The system consisted of an automated clipping
%%   and tagging framework that would cut up every single MLB game and episode of
%%   SportsCenter into each component play or segment and add most relevant
%%   metadata (i.e. what teams/people, what happens, etc.). The client displayed
%%   all this on a custom built iPad application that communicated with an Android
%%   app running on a GoogleTV allowing users to navigate through all the content
%%   (live) and choose where to watch it (iPad, any of several “cable boxes”/TVs).}

%% \project{MrEncoder / MrRest / NASAmatic}{I was the sole engineer implementing
%%   a production quality version of the custom HLS video server that powered
%%   TV2016 (above). This meant writing a Java HLS library capable of speaking all
%%   major versions of the HLS protocol and representing all the different metadata
%%   elements described by HLS (timing info, closed captions, etc.). This system
%%   was used to publish college sports clips by owning them through the process of
%%   ingestion (go from a satellite dish to something we can use), clipping (what
%%   part do I want?), tagging (who’s/what’s in it?), all the way to distribution
%%   (how do we get it to a CDN?). Using this system to clip and tag instead of
%%   expensive “edit seats” connected to a industry standard storage system
%%   (Quantel) dramatically increased the productivity of individuals: the
%%   “automatic” clipping capabilities were augmented to make the people
%%   responsible for clipping and tagging more accurate and more productive. In
%%   order to handle a special request from NASA, were asked to adapt this system
%%   to send SportsCenter, Around The Horn, and PTI, to the International Space
%%   Station}

%% \project{Semantic Databases}{I was the sole engineer trying to solve the
%%   problem: When one DB powers graphics systems, one DB powers espn.com, and one
%%   DB powers the statistical analysts, etc., and each database has its own unique
%%   ID for a common external entity (i.e. Michael Jordan had N different integer
%%   IDs across the company) , how can we tag content with entities in one system
%%   and understand them in the context another? In other words, I was tasked with
%%   figuring how to create a unique notion of identity across several data systems
%%   all describing the same world in slightly different ways.  I got as far as a
%%   proof-of-concept that could translate primary keys based on computing the
%%   similarity of “identity-facts” defined in terms of a common ontology about
%%   each entity in each database and doing a fuzzy-comparison.}


\end{document} 


